Code Clones: To refactor or not to refactor?

### 2020-05-09 ase/paper.tex
Updates from Overleaf

% How we fix the problem that we introduced in the first paragraph
We use software maintainability metrics to determine the impact of a refactoring applied to duplicate code. For a given refactoring we aggregate a set maintainability metrics (duplication, complexity, unit size, code volume) that are calculated on unit level. This score provides support for a developer to decide whether a given clone is likely to improve the codebase when refactoring.

% Experimental setup: how we validated that we fixed the problem
To simulate such refactorings in a controlled environment, we create a tool that can automatically refactor a subset of duplication problems in Java source code. Our tool refactors 13k clones over 2k open-source Java projects and measures the delta maintainability scores of the refactoring.

@@

\section{Survey of existing clone detection tools}\label{sec:survey}
%To detect refactorable clones according to the definitions introduced in Sec.~\ref{sec:research}, we survey existing clone detection tools for their suitability.
To investigate the impact of the definitions introduced in Sec.~\ref{sec:research}, we need a tool to detect refactorable clones according to these definitions. We conducted a short survey on (recent) clone detection tools to detect such clones that can be refactored. The results of our survey are displayed in table~\ref{table:dettools}. We chose a set of tools that are open source and can analyze a popular object-oriented programming language. Next, we formulate the following four criteria by which we analyze these tools:
\begin{enumerate}
    \item \textbf{Should find clones in any context.} Some tools only find clones in specific contexts, such as only method level clones. We want to perform an analysis of all clones in projects to get a complete overview.
\item \textbf{Finds clone classes in control projects.} We assembled a number of control projects to assess the validity of the surveyed clone detection tools.
\item \textbf{Can analyze resolved symbols.} When detecting the clones proposed in Sec.~\ref{sec:research}, it is important that we can analyze resolved symbols (for instance a type reference).
\item \textbf{Extensive detection configuration.} Detecting our clone definitions, as proposed in Sec.~\ref{sec:research}, require to have some understanding about the meaning of tokens in the source code (whether a certain token is a type, variable, etc.). The tool should recognize such structures, in order for us to configure our clone type definitions in the tool.
\end{enumerate}

>>>>

% How we fix the problem that we introduced in the first paragraph
We use software maintainability metrics to determine the impact of a refactoring applied to duplicate code. For a given refactoring we aggregate a set maintainability metrics (duplication, complexity, unit size, code volume) that are calculated on unit level, which we call the delta maintainability score. %This score provides support for a developer to decide whether a given clone is likely to improve the codebase when refactoring. 
Based on this score, we extract common factors between clones for a developer to filter their clone output based on the factors and the derived thresholds for them.

% Experimental setup: how we validated that we fixed the problem
To simulate such refactorings in a controlled environment, we create a tool that can automatically refactor a subset of duplication problems in Java source code. This subset is based on adapted clone definitions, that are optimized towards automated refactoring. Using these definitions we can extract a sufficiently large dataset of refactored clones to perform our analyses. Our tool refactors 13k clones over 2k open-source Java projects and measures the delta maintainability scores of the refactoring.

@@

\subsection{Survey of existing clone detection tools}\label{sec:survey}
%To detect refactorable clones according to the definitions introduced in Sec.~\ref{sec:research}, we survey existing clone detection tools for their suitability.
To investigate the impact of the definitions introduced in Sec.~\ref{sec:research}, we need a tool to detect refactorable clones according to these definitions. We conducted a short survey on (recent) clone detection tools to detect such clones that can be refactored. The results of our survey are displayed in table~\ref{table:dettools}. We chose a set of tools that are open source and can analyze a popular object-oriented programming language. Next, we formulate the following four criteria by which we analyze these tools:
\begin{enumerate}
    \item \textbf{Should find clones in any context.} Some tools only find clones in specific contexts, such as only method level clones. We want to perform an analysis of all clones in projects to get a complete overview.
\item \textbf{Finds clone classes in control projects.} We assembled a number of control projects to assess the validity of the surveyed clone detection tools.
\item \textbf{Can analyze resolved symbols.} When detecting the clones proposed in Sec.~\ref{sec:research}, it is important that we can analyze resolved symbols (for instance a type reference).
\item \textbf{Extensive detection configuration.} Detecting our clone definitions, as proposed in Sec.~\ref{sec:research}, require to have some understanding about the meaning of tokens in the source code (whether a certain token is a type, variable, etc.). The tool should recognize such structures, in order for us to configure our clone type definitions in the tool.
\end{enumerate}
